Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup

### 2013-06-24 snapshot_system/result.tex
Add performance analysis

>>>>

\subsection{System Performance}
{\bf Single VM Backup} We start the evauluation of our system by examine the normal warmed-up
backup scenario - taking a snapshot of a VM which already has old backups exist. To simulate this
scenario, we pick one 40GB VM from the data set, make an initial snapshot backup, then
evaulate the system performance on the second snapshot backup. We repeat such procedure
under different CDS memory usage settings, the results of backup time break down are shown in
firure~\ref{fig:single_vm_backup}.

It's easy to see that the time of I/O dominates the backup process, our deduplication
procedure only takes a tiny fraction of the total backup time. Larger memory permits us to
use larger CDS index to cover more of global index, as a result the amount of data to be writen
is reduced and so do the writing time.
Inside the deduplication procedure, the time costs of level-1
is plainly zero, and the costs of level-2 and level-3 are almost identical under different settings
because the number of fingerprints to process are just the same.
\begin{figure}[htbp]
  \centering
  \epsfig{file=figures/single_backup_time.pdf, width=3.5in}
  \caption{Time to backup a 40GB VM snapshot under different CDS memory usage settings}
  \label{fig:single_vm_backup}
\end{figure}

{\bf Parallel VM Backup} We then evaluate the performance of writing snapshots in parallel.
To begin, on each node we let 4 VMs writing snapshot concurrently, and gradually 
increase number of VMs to 12 to saturate our system capability. We observed 
the per-node throughput peaked at 2700 MB/s when writing 10 VM snapshots in parallel, 
which is far beyond our QFS file system capability. The reason behind it is our efficient
deduplication architecture and compression greatly reduce the amount of data that need to be writen to
the file system. The main bottleneck here is our QFS only manages one disk per node, 
making it inefficient to utilize the benefits of parallel disk access. We expect our achitecture can
perform even better in production cluster which normally has more than ten disks on each node.

\begin{figure}[htbp]
  \centering
  \epsfig{file=figures/parallel_backup.pdf, width=3.5in}
  \caption{Throughput per-node with concurrent snapshot backup tasks}
  \label{fig:parallel_backup}
\end{figure}

\subsection{Read Snapshot}
